Pathogen Spillover - dissertation chapter

### 2019-04-07 pathogen-spillover-diss-ch.Rmd
Revert to pre-conflict file.

# Updated SEM uses untransformed UMCA variables ####
# lfct is the ln(tot_lfct+1)
      # lmer(h2005 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),
m_list_update <- list(

            shannon.mod <- lm(h2005 ~ twi15m, data = filter(oaks.data, year==2006), na.action = na.omit),
      # changed the bay response to be log-transformed 
      umca.mod <- lmer(tot_bay.ln1 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),

@@

@@

# marginal effects of each significant predictor variable
cowplot::plot_grid(
inf.lfct.plot <- inf.lfct.plot +
      geom_point(data = oaks.data, 
                 aes(x = lfct, 
                     y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
                     ),
                 alpha = .1, size = 1),
# inf.lfct.plot +
#       geom_point(data = filter(oaks.data, inf_oak_ct/(inf_oak_ct+uninf_oak_ct) <.5), 
#                  aes(x = lfct, 
#                      y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
#                      ),
#                  alpha = .4, size = 1),

inf.h2005.plot <- plot_model(inf.mod, type = "pred", terms = c("h2005"), show.data = T) +
      geom_point(data = oaks.data, 
                 aes(x = h2005, 
                     y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
                     ),
                 alpha = .1, size = 1) +
      theme_classic() +
      xlab("Shannon's diversity index") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL,

inf.hrs1422.plot <- plot_model(inf.mod, type = "pred", terms = c("hrs1422")) +
      geom_point(data = oaks.data, aes(x = hrs1422, y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)), alpha = .1, size = 1) +
      theme_classic() +
      xlab("Hours 14-22 ºC") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL,
labels = "auto"
)

@@

(sig.rel.fig <- cowplot::plot_grid(
      inf.lfct.plot,
      inf.h2005.plot +
            xlab("Tree diversity (H')"),
      inf.hrs1422.plot,
      slc_vs_bay_plot +
            ggtitle(""),
      slc_vs_hrs25_plot +
            ggtitle(""),
      hot.mod.plot +
            ggtitle(""),
      shannon.plot +
            ggtitle(""),
      labels = "auto", label_x = .01
      )
)
ggsave("figures/path-significant-relationships.png", plot = sig.rel.fig,
       width = 7, height = 7, units = "in")

>>>>

# Updated SEM uses untransformed UMCA variables ####
# lfct is the ln(tot_lfct+1)
      # lmer(h2005 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),

test.mod <- lm(h2005 ~ twi15m, data = filter(oaks.data, year==2006), na.action = na.omit)

m_list_update <- list(

      shannon.mod <- lmer(h2005 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),
      # changed the bay response to be log-transformed 
      umca.mod <- lmer(tot_bay.ln1 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),

@@

test.psem <- psem(

      lmer(h2005 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),

      # lmer(tot_bay.ln1 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),
      # 
      # lmer(lfct ~ tot_bay.ln1 + hrs25 + hrs1422 + h2005 + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),
      # 
      # lmer(hrs1422 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),
      # 
      # lmer(hrs25 ~ twi15m + (1|plotid) + (1|year), data = oaks.data, na.action = na.omit),

      glmer(oakinf ~ lfct + hrs1422 + h2005 + (1|plotid) + (1|year), family = binomial(link = "logit"), data = oaks.data, na.action = na.omit)

@@

# marginal effects of each significant predictor variable

inf.lfct.plot <- inf.lfct.plot +
      geom_point(data = oaks.data, 
                 aes(x = lfct, 
                     y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
                     ),
                 alpha = .1, size = 1)
# inf.lfct.plot +
#       geom_point(data = filter(oaks.data, inf_oak_ct/(inf_oak_ct+uninf_oak_ct) <.5), 
#                  aes(x = lfct, 
#                      y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
#                      ),
#                  alpha = .4, size = 1),

inf.h2005.plot <- plot_model(inf.mod, type = "pred", terms = c("h2005"), show.data = T) +
      geom_point(data = oaks.data, 
                 aes(x = h2005, 
                     y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
                     ),
                 alpha = .1, size = 1) +
      theme_classic() +
      xlab("Shannon's diversity index") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL

inf.hrs1422.plot <- plot_model(inf.mod, type = "pred", terms = c("hrs1422")) +
      geom_point(data = oaks.data, aes(x = hrs1422, y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)), alpha = .1, size = 1) +
      theme_classic() +
      xlab("Hours 14-22 ºC") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL,

@@

(sig.rel.fig <- cowplot::plot_grid(
      inf.lfct.plot,
      inf.h2005.plot +
            xlab("Tree diversity (H')"),
      inf.hrs1422.plot,
      slc_vs_bay_plot +
            ggtitle(""),
      slc_vs_hrs25_plot +
            ggtitle(""),
      hot.mod.plot +
            ggtitle(""),
      shannon.plot +
            ggtitle(""),
      labels = "auto", label_x = .01
      )
)
ggsave("figures/Fig4-path_significant_relationships.png", plot = sig.rel.fig,
       width = 7, height = 7, units = "in", dpi=600)
